---
title: "Airport Stock Prediction git"
author: "Yoni"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    theme: united
---

# Setup and Data loading

## Libraries
```{r libraries, warning=F, message=F}
library(httr)
library(readr)
library(tidyverse)
library(fixest)
library(here)
set.seed(42)
```

I use [Alphavantage](https://www.alphavantage.co/documentation/) site for stock monthly information API query:
and the [Bureau of Transportation Statistics (BTS)](https://www.transtats.bts.gov/OT_Delay/OT_DelayCause1.asp) 
for of all carriers' monthly delay data.
fuel data from [Fred](https://fred.stlouisfed.org/series/WJFUELUSGULF#)

## Import data
```{r import data, warning=F, message=F,include= F}
loc_file<- "D:/for_Git_repository/Airport_stock/"
delay_data <- read_csv(here("data", "Airline_Delay_Cause_26.csv")) %>%
  filter(carrier %in% c("B6","DL","AS","HA", "F9", "AA", "UA","WN"))

delay_data<- delay_data %>%
  mutate(carrier= case_when(
    carrier== "B6" ~ "JBLU", #Jet Blue
    carrier== "DL" ~ "DAL",  #Delta Air Lines
    carrier== "AS" ~ "ALK",  #Alaska
    carrier== "HA" ~ "HA",   #Hawaiian Airlines
    carrier== "F9" ~ "ULCC", #Frontier
    carrier== "AA" ~ "AAL",  #American Airlines
    carrier== "UA" ~ "UAL",  #United Air Lines
    carrier== "WN" ~ "LUV"   #United Air Lines
, .default = as.character("else")))
write_csv(delay_data, here("data", "delay_data.csv"))
```

```{r read all from API}
#key<- read_csv(paste0(loc_file,"stock_api_key.csv")) %>% unlist()
#DAL_get<- paste0("https://www.alphavantage.co/query?function=TIME_SERIES_MONTHLY&symbol=DAL&apikey=",
#key,"&datatype=csv") %>% GET()
#UAL_get<- paste0("https://www.alphavantage.co/query?function=TIME_SERIES_MONTHLY&symbol=UAL&apikey=",
#key,"&datatype=csv") %>% GET()
#JBLU_get<- paste0("https://www.alphavantage.co/query?function=TIME_SERIES_MONTHLY&symbol=JBLU&apikey=",
#key,"&datatype=csv") %>% GET()
#AAL_get<- paste0("https://www.alphavantage.co/query?function=TIME_SERIES_MONTHLY&symbol=AAL&apikey=",
#key,"&datatype=csv") %>% GET()
#ALK_get<- paste0("https://www.alphavantage.co/query?function=TIME_SERIES_MONTHLY&symbol=ALK&apikey=",
#key,"&datatype=csv") %>% GET()
#HA_get<- paste0("https://www.alphavantage.co/query?function=TIME_SERIES_MONTHLY&symbol=HA&apikey=",
#key,"&datatype=csv") %>% GET()
#ULCC_get<- paste0("https://www.alphavantage.co/query?function=TIME_SERIES_MONTHLY&symbol=ULCC&apikey=",
#key,"&datatype=csv") %>% GET()
#LUV_get<- paste0("https://www.alphavantage.co/query?function=TIME_SERIES_MONTHLY&symbol=LUV&apikey=",
#key,"&datatype=csv") %>% GET()
```

```{r save api, echo = FALSE}
#writeBin(content(DAL_get, "raw"),here("data", "DAL_month.csv" ))
#writeBin(content(UAL_get, "raw"),here("data", "UAL_month.csv" ))
#writeBin(content(JBLU_get,"raw"),here("data", "JBLU_month.csv"))
#writeBin(content(AAL_get, "raw"),here("data", "AAL_month.csv" ))
#writeBin(content(ALK_get, "raw"),here("data", "ALK_month.csv" ))
#writeBin(content(HA_get,  "raw"),here("data", "HA_month.csv"  ))
#writeBin(content(ULCC_get,"raw"),here("data", "ULCC_month.csv"))
#writeBin(content(LUV_get, "raw"),here("data", "LUV_month.csv" ))
```

```{r import airport CSV stock, message=F, error=F,include= F}
delay_data<- read_csv(here("data", "delay_data.csv")) 

DAL<- read_csv(here("data","DAL_month.csv")) %>%
  mutate(Carrier= "DAL")
UAL<- read_csv(here("data","UAL_month.csv")) %>%
  mutate(Carrier= "UAL")
JBLU<- read_csv(here("data","JBLU_month.csv")) %>%
  mutate(Carrier= "JBLU")
AAL<- read_csv(here("data","AAL_month.csv")) %>%
  mutate(Carrier= "AAL")
ALK<- read_csv(here("data","ALK_month.csv")) %>%
  mutate(Carrier= "ALK")
HA<- read_csv(here("data","HA_month.csv")) %>%
  mutate(Carrier= "HA")
ULCC<- read_csv(here("data","ULCC_month.csv")) %>%
  mutate(Carrier= "ULCC")
LUV<- read_csv(here("data","LUV_month.csv")) %>%
  mutate(Carrier= "LUV")

carrier_names<-  read_csv(here("data","Airline_Delay_Cause_26.csv")) %>% 
  dplyr::select(carrier,carrier_name) %>%
  distinct(carrier, .keep_all = TRUE) %>% 
  arrange(carrier)
```

# Data handeling

## Data cleaning

```{r read airport CSV stock, message=F, error=F,include= F}
fuel_df<- read_csv(here("data","jet_fuel_data.csv")) %>% 
  mutate(month= month(observation_date),
         year= year(observation_date)) %>% 
  rename(Fuel_price= WJFUELUSGULF) %>% 
  arrange(observation_date) %>%
  mutate(fuel_del = (Fuel_price / lag(Fuel_price) - 1)) %>% 
  select(-observation_date )
```

```{r choose carier, message=F, error=F,include= F}
read_csv(here("data","Airline_Delay_Cause_26.csv"))%>% 
  select(carrier,arr_flights) %>% 
  group_by(carrier) %>%
  summarise(total_flights = sum(arr_flights, na.rm = TRUE)) %>% 
  arrange(desc(total_flights)) %>% 
  ungroup() %>% left_join(carrier_names )
```

```{r create stock data & preview}
all_stock<- bind_rows(DAL,UAL,JBLU,AAL,ALK, HA, ULCC,LUV) %>% 
  rename(S_Date= timestamp) %>% 
  mutate(month= month(S_Date),
         M_day= day(S_Date),
         year= year(S_Date)) 

rm(DAL,UAL,JBLU,AAL,ALK, HA, ULCC,LUV)  
```

### Combine all Data

```{r combine all data, message=F, error=F,include= F}
av_delay_df<-
  delay_data %>% 
  select(airport,carrier,year, month, arr_delay, arr_flights) %>%
  group_by(carrier, year, month) %>%
  summarise(
    arr_delay = sum(arr_delay, na.rm = TRUE),
    arr_flights = sum(arr_flights, na.rm = TRUE),
    .groups = "drop"
  ) %>%  
  mutate(av_delay= arr_delay/arr_flights) %>% 
  left_join(all_stock, join_by(carrier== Carrier, year== year, month== month), relationship = "many-to-many") %>%
  filter(S_Date>= "2002-01-01" & S_Date<= "2025-11-01") %>% 
  mutate(grow= (close-open)/open,
         grow_log= close/open,
         post_corona= (year>= 2020 & month>= 3) | year>= 2021,
         decade= factor((year-2000) %/% 10)) %>% 
    left_join(fuel_df, join_by(year== year, month== month), relationship = "many-to-many") %>% 
  drop_na()

av_delay_df %>% slice_sample(n=6) %>% write_csv(here("data","av_delay_df_ex.csv"))
```

```{r panel data}
av_delay_df %>%
  group_by(carrier) %>%
  summarise(
    Start = min(S_Date, na.rm = TRUE),
    End = max(S_Date, na.rm = TRUE),
    Observations = n()
  )
```

# Exploratory Data Analysis (EDA)

```{r}
modelsummary::datasummary_skim(av_delay_df)
```
## correlation graphs

```{r ally, message=F, error=F}
av_delay_df %>%
  mutate(month= as.factor(month)) %>% 
  select(8:11,14,19) %>% 
GGally::ggpairs()
```

### Growth Correlation
```{r growth correlation, message=F, error=F,include= F}
monthly_growth <- all_stock %>%
  mutate(growth = (close - open) / open) %>% 
  group_by(Carrier, year, month) %>%
  summarise(
    monthly_growth = mean(growth, na.rm = TRUE)
  ) %>%
  ungroup()

growth_wide <- monthly_growth %>%
  mutate(period = paste(year, month, sep = "-")) %>%
  select(period, Carrier, monthly_growth) %>%
  pivot_wider(names_from = Carrier, values_from = monthly_growth)

cor(
  growth_wide %>% select(-period),
  use = "pairwise.complete.obs"
) %>% 
  round(3) %>% 
  as.data.frame()
```

### data density

```{r graph time corona, message=F, error=F}
all_stock %>%
  filter(S_Date>= "2002-01-01") %>% 
  ggplot(aes(x= S_Date, y= close, color= Carrier))+
  geom_line()+
  geom_vline(xintercept =as.numeric(date("2020-02-01")), linetype=2)+ #add corona line
    scale_x_date(
    date_breaks = "2 year",
    date_labels = "%Y"
  )+
    labs(
    title = "Stock Value at Close Over Time",
    x = "Date",
    y = "Price ($)", color = "Carrier"
  )+
    annotate(
    "text",
    x = as.Date("2020-02-01") + 150,   #move to the right
    y = max(all_stock$close, na.rm = TRUE) * 0.95,  #near top of chart
    label = "COVID-19", color = "red", size = 2
  )+
   theme(legend.position="bottom")
```

```{r averege grow, message=F, error=F}
feols(
  grow ~ year | Carrier + factor(month),
  data = (all_stock %>% 
            mutate(grow= close/open)),
  cluster = ~ Carrier)
```

### Month effect

```{r av late by month, message=F, error=F}
delay_data %>%
select(airport,carrier,year, month, arr_delay, arr_flights) %>%
  group_by(month) %>%
  summarise(
    arr_delay = sum(arr_delay, na.rm = TRUE),
    arr_flights = sum(arr_flights, na.rm = TRUE),
    .groups = "drop"
  ) %>%  
  mutate(av_delay= arr_delay/arr_flights) %>% 
  select(-arr_delay,-arr_flights)
```

```{r by month graphs, message=F, error=F}
av_delay_df %>%
  ggplot(aes(x= factor(month), y= grow, fill= factor(month)))+
  geom_violin(alpha= 0.4, draw_quantiles = 0.5)+
    labs(
    title = "Stock Growth by Month",
    x = "av delay",
    y = "growth",
    color = "Carrier"
  )

av_delay_df %>%
  group_by(year, month) %>%
  summarise(
    mean_grow = mean(grow, na.rm = TRUE),
    .groups = "drop"
  ) %>% 
  ggplot(aes(x = factor(year), y = factor(month), fill = mean_grow)) +
  geom_tile(color = "white") +
  #scale_fill_viridis_c(option = "plasma") +
  scale_fill_gradient2(
    low  = "red4",    # ערכים שליליים
    mid  = "grey70",  # אפס (או המרכז)
    high = "green4",  # ערכים חיוביים
    midpoint = 0
  )+
  labs(
    title = "Average Grow by Month and Year",
    x = "Year",
    y = "Month",
    fill = "Mean Grow"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
```

```{r try visual lm, message=F, error=F}
av_delay_df %>%
  ggplot(aes(x= S_Date, y= av_delay, color= carrier))+
  geom_smooth(se= F, span = 0.09 )+
    labs(
    title = "avarege latency over Time",
    x = "av delay",
    y = "growth",
    color = "Carrier"
  )+
  geom_vline(xintercept =as.numeric(date("2020-02-01")), linetype=2)+ #add corona line
    annotate(
    "text",
    x = as.Date("2020-02-01") + 150,   # move slightly to the right (adjust as needed)
    y = max(av_delay_df$av_delay-15, na.rm = TRUE) * 0.95,  # near top of chart
    label = "COVID-19", color = "red", size = 2
  )
```

```{r, message=F, error=F}
av_delay_df %>%
  ggplot(aes(x= Fuel_price, y= grow))+
  geom_point(alpha= 0.8, aes(color= carrier))+
  geom_smooth(se= F, color= "grey30")+
    labs(
    title = "avarege fuel price vs Stock growth",
    x = "fuel price",
    y = "growth"
    )+
  theme(panel.grid = element_line(color = "grey70"))
```

### LM by carrier

```{r, message=F, error=F}
av_delay_df %>%
  ggplot(aes(x= av_delay, y= grow, color= carrier))+
  geom_point(alpha= 0.6)+
  geom_smooth(method = "lm", se= F, color= "Black")+
    labs(
    title = "LM model by carrier",
    x = "delay",
    y = "growth",
    color = "Carrier"
  )+facet_wrap(~carrier)

lm_carrier_table <- bind_rows(
  lapply(
    split(av_delay_df, av_delay_df$carrier),
    function(df) {
      model <- lm(grow ~ av_delay, data = df)
      s <- summary(model)
      
      data.frame(
        Carrier   = unique(df$carrier),
        Intercept = round(coef(model)[1], 4),
        av_delay  = round(coef(model)[2], 4),
        R2        = round(s$r.squared, 4),
        Adj_R2    = round(s$adj.r.squared, 4),
        p_value   = round(s$coefficients[2, "Pr(>|t|)"], 4),
        N         = nrow(df), row.names = unique(df$carrier)
      )
    }
  )
)
lm_carrier_table
#lm_carrier_table %>% write_csv(here("data","Carrier_pred.csv"))
```

```{r, message=F, error=F}
long_df <- av_delay_df %>%
  select(S_Date, Fuel_price, close) %>%
  mutate(Fuel_price= Fuel_price) %>% 
  pivot_longer(cols = c(Fuel_price, close),
               names_to = "variable",
               values_to = "close")
```

```{r Fuel Price and Growth over Time, message=F, error=F}
long_df %>%
  ggplot(aes(x = S_Date, y = close, color = variable)) +
  geom_point(alpha = 0.5)+
  geom_smooth(se= F, span= 0.2,degree= 2, aes(type= variable), color= "grey40")+
  labs(
    title = "Fuel Price and Growth over Time",
    x = "Date",
    y = "Value",
    color = "Variable"
  )+
    theme(legend.position = "bottom")+ facet_wrap(~variable, nrow= 2, scales= "free_y")
```

```{r late hist, message=F, error=F}
ggplot(av_delay_df, aes(x = grow_log,fill= carrier)) +
  geom_density(bins = 40,alpha = 0.8) +
  facet_wrap(~carrier, nrow= 2)+
  labs(
    title = "Distribution of Monthly Stock Returns",
    x = "Monthly return (%)",
    y = "Count"
  )
```

```{r late dencity pro, message=F, error=F}
mean_df <- av_delay_df %>%
  group_by(carrier) %>%
  summarise(mean_delay = mean(av_delay, na.rm = TRUE),
            xmin = min(av_delay, na.rm = TRUE),
            xmax = max(av_delay, na.rm = TRUE)) %>% 
  mutate(label = paste0("\u03BC = ", round(mean_delay, 1)),
          x_mid = (xmin + xmax) / 2)

#mean_df %>% write_csv(here("data","late_mid_av.csv"))

ggplot(av_delay_df, aes(x = av_delay, fill = carrier)) +
  geom_density(adjust = 1/2, alpha = 0.7) +
  facet_wrap(~carrier, nrow = 2) +
  geom_vline(data = mean_df, aes(xintercept = mean_delay),
    color = "blue3",
    linetype = "dashed") +
  labs(
    title = "Distribution of Average Delay by Carrier",
    x = "Delay (mean)") +
  theme_minimal()+
geom_text(
  data = mean_df,
  aes(x = x_mid, y = Inf, label = label),
  vjust = 2,
  hjust = 0.5,
  color = "red")
```

```{r late by reason}
delay_long<-
  delay_data %>% 
  select(carrier, year, month,
         carrier_delay, weather_delay, nas_delay,
         security_delay, late_aircraft_delay) %>%
  pivot_longer(
    cols = c(carrier_delay, weather_delay, nas_delay,
         security_delay, late_aircraft_delay),
    names_to = "Reason",
    values_to = "Delay_Min"
  ) %>% 
    mutate(
    Reason = gsub("_delay$", "", Reason, ignore.case = TRUE)
  )

delay_share <- delay_long %>%
  group_by(carrier, Reason) %>%
  summarise(
    Total_Delay = sum(Delay_Min, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  group_by(carrier) %>%
  mutate(
    Share = Total_Delay / sum(Total_Delay)
  )
```

```{r plot reason}
ggplot(delay_share,
       aes(x = Share,
           y = carrier,
           fill = Reason)) +
  geom_col(position = "fill", alpha = 0.9) +
  scale_x_continuous(labels = scales::percent_format()) +
  labs(
    title = "Delay Composition by Airline",
    x = "Percentage of Total Delays",
    y = "Airline",
    fill = "Delay Reason"
  ) +
  theme_minimal()+
theme(panel.grid = element_line(color = "grey30"))
```

```{r plot reason 2}

delay_long %>%
  mutate( decade= factor((year-2000) %/% 10) )%>% 
  group_by(decade, Reason) %>%
  summarise(
    Total_Delay = sum(Delay_Min, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  group_by(decade) %>%
  mutate(
    Share = Total_Delay / sum(Total_Delay)
  ) %>% 
ggplot(aes(x = Share,
           y = decade,
           fill = Reason)) +
  geom_col(position = "fill", alpha = 0.9) +
  scale_x_continuous(labels = scales::percent_format()) +
  labs(
    title = "Delay Composition by Decade",
    x = "Percentage of Total Delays",
    y = "Decade",
    fill = "Delay Reason"
  ) +
  theme_classic()+
theme(panel.grid = element_line(color = "grey70"))
```


# Modeling

## Main Model

```{r prediction fun simply lm}
glm_stock_simple <- glm(log(grow_log) ~ av_delay + factor(month) + carrier,
                        data = av_delay_df,
                        family = gaussian())
```

```{r summary main model}
summary(glm_stock_simple)

glm_stock_simple %>% plot()
```


```{r pred vs reality}
pred_simple <- tibble::tibble(
  prediction = exp(fitted(glm_stock_simple)),
  growth     = model.response(model.frame(glm_stock_simple)),
  Carrier    = model.frame(glm_stock_simple)$carrier,
  Date       = glm_stock_simple$data$S_Date
) |>
  mutate(
    pred_delta = growth - prediction
  )

pred_simple |>
  pivot_longer(cols = c(prediction, growth),
               names_to = "type",
               values_to = "value")%>% 
ggplot(aes(x = Date, y = value, color = type)) +
  geom_line() +
  facet_wrap(~ Carrier, scales = "free_y") +
  labs(
    title = "Predicted vs Actual Growth Over Time",
    x = "Date",
    y = "Growth"
  ) +
  theme_minimal()

pred_simple |>
ggplot(aes(x = Date, y = pred_delta)) +
  geom_line() +
  facet_wrap(~ Carrier, scales = "free_y") +
  labs(
    title = "Unpredicted Actual Growth Over Time",
    x = "Date",
    y = "Unpredicted Growth"
  ) +
  theme_minimal()
```

## Main model's stability test

```{r heteroskedasticity test}
lmtest::bptest(glm_stock_simple)
```

A Breusch-Pagan test strongly rejected the null hypothesis of homoskedasticity (BP = 63.01, p < 0.001), indicating the presence of heteroskedasticity. Therefore, heteroskedasticity-robust standard errors were employed in all subsequent regression.

```{r multicollinearity}
car::vif(glm_stock_simple)
```

Variance Inflation Factors (VIF) were computed to assess multicollinearity. All values were below 5(even 2), indicating no severe multicollinearity concerns.

Robustness Checks

To verify the validity of the empirical results, several robustness checks were conducted. A Breusch–Pagan test indicated the presence of heteroskedasticity; therefore, all models were estimated using heteroskedasticity-robust standard errors. In addition, given the panel structure of the data (airlines observed over time), standard errors were clustered at the airline level to account for potential within-firm serial correlation.

Furthermore, alternative model specifications were estimated to test the stability of the main findings. In particular, a lagged delay specification was implemented to examine whether stock returns respond to operational performance with a temporal delay. The estimated coefficients remain stable in sign and magnitude across specifications, supporting the robustness of the central empirical results.

### Fix Main Model

Pooled OLS may confound cross-sectional differences with within-firm effects; therefore a fixed-effects estimator is employed.

```{r fixest}
model_stock_fixest <- feols(
  log(grow_log) ~ av_delay | carrier + month,
  data = av_delay_df,
  cluster = ~ carrier
)

summary(model_stock_fixest)
```

## Alternative models

### Fuel effect

```{r prediction fun simplefy+ fuel}
model_fuel_fixest <- feols(
  log(grow_log) ~ av_delay + fuel_del| carrier + month,
  data = av_delay_df,
  cluster = ~ carrier
)

summary(model_fuel_fixest)
```


### On Time instead of late

```{r coock "on_time" percent}
av_delay_df_on_time<-
  delay_data %>% 
  select(airport,carrier,year, month, arr_delay, arr_flights, arr_del15, arr_cancelled,	arr_diverted) %>%
  group_by(carrier, year, month) %>%
  summarise(
    arr_flights = sum(arr_flights, na.rm = TRUE),
    not_on_time = sum(arr_del15+ arr_cancelled +	arr_diverted, na.rm = TRUE),
    .groups = "drop"
  ) %>% 
  mutate(on_time_pr= (arr_flights-not_on_time)/arr_flights) %>% 
  left_join(all_stock, join_by(carrier== Carrier, year== year, month== month), relationship = "many-to-many") %>%
  filter(S_Date>= "2002-01-01" & S_Date<= "2025-11-01") %>% 
  mutate(grow= (close-open)/open,
         grow_log= close/open,
         post_corona= (year>= 2020 & month>= 3) | year>= 2021,
         decade= (year-2000) %/% 10)
```

```{r prediction fun on_time simplefy}
model_on_time_fixest <- feols(
  log(grow_log) ~ on_time_pr | carrier + month,
  data = av_delay_df_on_time,
  cluster = ~ carrier
)

summary(model_on_time_fixest)
```

```{r Time of year+ month}
model_stock_fixest_ym <- feols(
  log(grow_log) ~ av_delay | carrier + month+ year,
  data = av_delay_df,
  cluster = ~ carrier
)

summary(model_stock_fixest_ym)
```

### lag model

```{r prediction fun with lag 3}
lag_data <- av_delay_df %>%
  arrange(carrier, S_Date) %>%
  group_by(carrier) %>%
  mutate(
    delay_lag1 = lag(av_delay, 1),
    delay_lag2 = lag(av_delay, 2),
    delay_lag3 = lag(av_delay, 3)
  ) %>%
  ungroup() %>%
  drop_na(delay_lag1, delay_lag2, delay_lag3)

lag_on_time <- av_delay_df_on_time %>%
  arrange(carrier, S_Date) %>%
  group_by(carrier) %>%
  mutate(
    time_lag1 = lag(on_time_pr, 1),
    time_lag2 = lag(on_time_pr, 2),
    time_lag3 = lag(on_time_pr, 3)
  ) %>%
  ungroup() %>%
  drop_na(time_lag1, time_lag2, time_lag3)


model_stock_lag3 <- feols(
  log(grow_log) ~ av_delay + delay_lag1 + delay_lag2 + delay_lag3|
                  month + carrier,
  data   = lag_data,
  cluster = ~ carrier
)
 
summary(model_stock_lag3)
```

## Compare all models

```{r compare base models}
models<- list(model_stock_fixest,model_fuel_fixest,model_on_time_fixest,model_stock_fixest_ym,model_stock_lag3)
names(models)<-   c("fixest_C_M", "fixest_C_M+Fuel", "fixest_C_M on time", "fixest_C_M_Y", "fixest_C_M lag3") 
modelsummary::modelsummary(models, title = "model 2-6 values")
```

first, lets compare the models with a filtered data, that omit the first 3 rows of each carrier in order to compare equal observation compering.

```{r create without lag}
model_stock_fixest_rl  <- feols(log(grow_log) ~ av_delay | carrier + month,
                                data = lag_data, cluster = ~carrier)

model_fuel_fixest_rl    <- feols(
  log(grow_log) ~ av_delay + fuel_del| carrier + month,
  data = lag_data,
  cluster = ~ carrier
)

model_on_time_fixest_rl <- feols( log(grow_log) ~ on_time_pr | carrier + month,
  data = lag_on_time, cluster = ~ carrier)

model_stock_fixest_ym_rl <- feols(
  log(grow_log) ~ av_delay | carrier + month+ year,
  data = lag_data,
  cluster = ~ carrier
)
```


```{r compare visuals}
models<- list(model_stock_fixest_rl,model_fuel_fixest_rl,model_on_time_fixest_rl,model_stock_fixest_ym_rl,model_stock_lag3)
names(models)<-   c("fixest_C_M", "fixest_C_M+Fuel", "fixest_C_M on time", "fixest_C_M_Y", "fixest_C_M lag3") 
cat("\n--- Model Comparison (equal sample) ---\n")
modelsummary::modelsummary(models, title = "models 2-6 lag cpmpare")
```

Using the $AIC$ model, the Fixed effect model by carrier, year and month looks to be the better one.

the final model (without lag obsservation omiting)
```{r}
summary(model_stock_fixest_ym)
```

